---
title: "p8105_hw1_crd2162"
output: github_document
date: "2023-09-18"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Problem 1


```{r}
library (moderndive)
library (tidyverse)
data ("early_january_weather")
```

The dataset early_january_weather contains early January hourly weather data for LGA, JFK, and EWR for the month of January 2013. The dataset contains `r ncol(early_january_weather)` variables and `r nrow(early_january_weather)` rows of observations. The variables included in the dataset are `r colnames(early_january_weather)`.

We will be analyzing the variables of temp, time_hour, and humid. Their values are as follows:

```{r}
early_january_weather$temp
early_january_weather$time_hour
early_january_weather$humid
```

The mean temperature in our dataset is `r mean(early_january_weather$temp)`

Now we will make a scatterplot comparing temp and time_hour with color points indicating humidity:

```{r}
plot_weather = tibble(
  x = early_january_weather$time_hour,
  y = early_january_weather$temp
  )

ggplot(plot_weather, aes(x = x, y = y, color = early_january_weather$humid)) + geom_point()
```





## Problem 2



```{r pressure, echo=FALSE}
plot(pressure)
```


